\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry} % Adjust page margins
\usepackage{enumitem} % Customize list environments

% Adjust page margins
\geometry{a4paper, margin=1in}

% Customize list environments
\setlist[itemize]{label=--}

\title{PIT Assignment 02}
\author{Jawad Ahmed (20P-0165) \\ Section: BCS-6A}
\date{October 2023}

\begin{document}

\maketitle

\section{Incorporation Name of the Company}
\textbf{Ans:} The company's incorporation name is \textbf{Systems Limited}. It's a leading Pakistani IT company founded in 1977, headquartered in Lahore, offering software development, consulting, and more.

\section{Registered Office of the Company}
\textbf{Ans:} The registered office is located at:
\begin{quote}
Systems Limited\\
Systems Campus, Lahore Software Technology Park,\\
E-1, Sehjpal Near DHA Phase-VIII,\\
Lahore Cantt, Pakistan
\end{quote}

\section{Incorporation Date}
\textbf{Ans:} Systems Limited was incorporated on \textbf{May 4, 1977}, as per the Securities and Exchange Commission of Pakistan (SECP).

\section{Type of Liability}
\textbf{Ans:} Systems Limited is a limited company, which means shareholders' liability is limited to their investment.

\section{Share Capital, Total Shares, and Cost per Share (Starting)}
\textbf{Ans:} Systems Limited is a public limited company listed on the Pakistan Stock Exchange. It started with a share capital of \textbf{Rs. 1 million}, \textbf{100 million} total shares, and a variable cost per share (currently around \textbf{Rs. 100}).

\section{Current Share Capital, Total Shares, and Cost per Share}
\textbf{Ans:} As per the Pakistan Stock Exchange (PSX) website, the current data for Systems Limited is as follows:
\begin{itemize}
    \item Market Capitalization: \textbf{Rs. 117.96 billion}
    \item Total Number of Shares: \textbf{290.26 million}
    \item Cost per Share: \textbf{Rs. 406.38}
\end{itemize}

\section{Terms Defined for Working of Directors}
\textbf{Ans:} Directors of Systems Limited, being a public company in Pakistan, must adhere to the Companies Act, 2017. This includes acting in the company's best interests, exercising diligence, avoiding conflicts of interest, declaring financial interests, and complying with specific rules for appointment, remuneration, borrowing powers, transactions with related parties, and disclosure.

\end{document}
